\section{Conclusion}
\label{sec:conc}

Blockchains have the potential to disrupt incumbent applications on the data sharing economy. In addition to this, the
Transportation industry is going through a radical shift due to the new types of data and applications that have become
available. For instance the proliferation of mobile phones has brought a surge in crowd-sourced data. Also widespread
deployment of cheap hardware sensor networks combined with smart analysis and planning algorithms are able to utilize this
data to create valuable new insights and applications that were not previously possible.

By bringing the blockchain technology and designing it from the grounds up for Transportation applications, we have created
the world's first blockchain specifically tailored for Transportation applications. Our mission is for Latitude to become
the de-facto platform for all transportation applications by building the right constructs for trusted, privacy-aware,
secure and verifiable data and computation sharing/enforcement.

Our mission is to build Latitude to support applications across the planet and across different modes of transport. We
are excited by how Latitude stands to disrupt existing applications such as Ride-sharing, Mapping, Location sharing and
analytics and the driver-behavior industry (UBIs).

The full-whitepaper shall contain a deeper dive into the mechanics of the Latitude blockchain including details on how
the smart contract system, the cryptographic proofs and the datastore would function.
