\begin{declaration}
\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents

\begin{itemize}
\item This is a conceptual document (“White Paper”) describing the Latitude platform and LAT tokens. It may be amended or
replaced at any time. However, there is no obligation to update the White Paper or to provide the recipient with access
to any additional information.

\item This White Paper does not constitute an investment, legal, tax, regulatory, financial, accounting or other advice, and
this White Paper is not intended to provide the sole basis for any evaluation of a transaction on acquiring of the
Latitude tokens. Prior to acquiring the Latitude tokens, a prospective purchaser should consult with his/her own legal,
investment, tax, accounting, and other advisors to determine the potential benefits, burdens, and other consequences of
such transaction.

\item Nothing in this White Paper shall be deemed to constitute a prospectus of any sort or a solicitation for investment, nor
does it in any way pertain to an offering or solicitation of an offer to buy any securities in any jurisdiction. This
document is not composed in accordance with, and is not subject to, laws or regulations of any jurisdiction which
prohibits or in any manner restricts transactions in respect of, or with use of, digital tokens.

\item The Latitude Blockchain or the token are not a digital currency, security, commodity, or any other kind of financial
instrument and has not been registered under the Securities Act of 1933, the securities laws of any state of the United
States of America or the securities laws of any other country, including the securities laws of any jurisdiction in
which a potential token holder is a resident.  No representations or warranties are made as to the accuracy or
completeness of the information, statements, opinions or other matters described in this document or otherwise
communicated in connection with the project.

\item Without limitation, no representation or warranty is given as to the achievement or reasonableness of any
forward-looking or conceptual statements. Nothing in this document is or should be relied upon as a promise or
representation as to the future. To the fullest extent permitted under applicable law, all liability for any loss or
damage whatsoever (whether foreseeable or not) arising from or in connection with any person acting on this White Paper,
or any aspect of it, notwithstanding any negligence, default or lack of care, is disclaimed. To the extent liability may
be restricted but not fully disclaimed, it is restricted to the maximum extent permitted by applicable law.

\item This White Paper is provided in an official English version only. White Paper may from time to time be translated into
other languages. Any translation is for reference purposes only and is not certified by any person. In the event of any
conflicts or inconsistencies between such translations and the official English language White Paper, the provisions of
the English language original document shall prevail. 
\end{itemize}

\noindent Date:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
\end{declaration}
