\documentclass[preprint,10pt]{elsarticle}
\usepackage{etoolbox}
\makeatletter
\patchcmd{\ps@pprintTitle}{\footnotesize\itshape
       Preprint submitted to \ifx\@journal\@empty Elsevier
       \else\@journal\fi\hfill\today}{06.2018}{}{}
\makeatother

\usepackage[margin=2.5cm]{geometry}

\newcommand{\fscale}[1]{#1\linewidth}
\newcommand{\figref}[1]{Fig.~\ref{#1}}

%-----------------------------------------------------------------------------
%  Colors
%-----------------------------------------------------------------------------
\usepackage{pagecolor}
\definecolor{linen}{RGB}{240,240,230}
\definecolor{fwhite}{RGB}{255,250,240}
\definecolor{oldlace}{RGB}{253,245,230}
\definecolor{awhite}{RGB}{250,235,215}
\definecolor{pwhip}{RGB}{255,239,213}
\definecolor{peach}{RGB}{255,218,185}
\definecolor{ivory}{RGB}{255,255,240}
\definecolor{seashell}{RGB}{	255,245,238}

\usepackage{sectsty}
\sectionfont{\Large \textsf}
\subsectionfont{\large \textsf}

\usepackage{amsmath}
\newcommand{\mr}[1]{\mathrm{#1}}  % Roman font for the math mode
\newcommand{\mi}[1]{\mathit{#1}}  % Italic font for the math mode
\newcommand{\mc}[1]{\mathcal{#1}} % Caligrafic (script) font for the math mode
\newcommand{\ms}[1]{\mathsf{#1}}  % Sans font for the math mode (vectors and matrices)
\newcommand{\mb}[1]{\mathbf{#1}}  % Bold font for the math mode (vectors and matrices)

\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{remark}{Rule}[section]

\newtheorem{property}{Property}

\newtheorem{theorem}{Theorem}

\usepackage{cleveref}
\crefformat{section}{\textbf{\S#2#1#3}} % see manual of cleveref, section 8.2.1
\crefformat{subsection}{\textbf{\S#2#1#3}}
\crefformat{subsubsection}{\textbf{\S#2#1#3}}

\renewcommand{\cref}[1]{\textbf{\S\ref{#1}}}

\usepackage{graphicx}
\usepackage{subfigure}
\graphicspath{{./fig/}}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}

\usepackage[titletoc]{appendix}
\usepackage[T1]{fontenc}

\usepackage{xcolor, soul}
\sethlcolor{oldlace}

\usepackage{lineno}
\usepackage{url}
\bibliographystyle{unsrt}

\patchcmd{\abstract}{Abstract}{Summary}{}{}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

\title{\textsf{Latitude: A Blockchain for the Transportation Industry\tnoteref{title1}}}
\tnotetext[title1]{Version 1.1}

\author{Arunesh Mishra, Latitude Labs\corref{auth1}}
\cortext[auth1]{Advisor/Consultant, Latitude Labs at https://latitude0x.com}
\address{Silicon Valley, California}

\begin{abstract}

Blockchains are rapidly becoming the new vehicles for decentralized applications for the data sharing economy. By their
    design, they are able to create privacy aware, secure, trusted, verifiable and user incentivized ways of sharing
    data. This ability has created a new wave of applications in various industries which are disrupting the status quo
    of the incumbents. Also, the Transportation industry is seeing a shift in terms of the amount of data that has
    become available due to mobile phones, dedicated sensors and crowdsourced availability of data. The industry has a
    large number of applications, users and regulations which can benefit from data sharing if it can be done correctly.

 We present the Latitude blockchain which is designed to be the best blockchain for transportation applications.
    Latitude is designed using principles derived from the core decentralized blockchain technologies available today
    combined with fundamental considerations for the unique aspects of Transportation data and applications. Latitude
    includes the world's first smart contract system specifically tailored for geo-spatial, mapping, location and sensor
    data and related applications. The system is powered by a geo-spatial decentralized datastore which can scale to
    planet level storage capabilities incentivized by a token economics built over the LAT (Latitude Token).

    The Latitude network is also provisioned with a library of algorithms, both open source and closed form, which allow
    Government, insurance companies and regulators to compute, certify and create cryptographic proofs which can help enforce policies
    or verify contracts.  Latitude has a decentralized Governance model using a Council system which is resistant to
    collusion and Byzantine behavior and is incentivized to maintain honest and proper operation of the network.

    Latitude can support four classes of applications. First, Ridesharing applications consist of the sharing economy
    applications for multi-modal ridesharing and transport. Using Latitude, it becomes possible to create better
    incentives for ride providers and users including incentives for data sharing and route optimizations. This also
    allows regulatory bodies to participate in the execution of these applications using smart contracts. Second,
    Telematics applications such as Usage-based Insurance (UBIs) and fleet management can benefit from real-time or
    historial data and corresponding intelligent algorithms, thus providing shared mutual benefits. The third class of
    application include mapping and location.  Using tangible user incentives while providing strong trust, privacy and
    security for user data, it is possible to create new or better data sharing applications (similar to Waze among
    others) on the Latitude platform. Finally, all the geo-spatial, location, mapping and real-time city level data can be used by the City and State
    governments for smart city applications to provide a better quality of life for their citizens.
\newline \newline \newline \end{abstract}

\begin{keyword}
	\textsf{location \sep cryptography\sep decentralization \sep blockchain \sep ethereum \sep database \sep sql
    \sep access control \sep p2p \sep tokens \sep incentives \sep mechanism design \sep byzantine
    faults \sep data sharing \sep latitude \sep longitude \sep driverscore \sep mapping \sep transportation \sep
    insurance}
\end{keyword}

\end{frontmatter}

\newpage
\tableofcontents
\newpage

%-----------------------------------------------------------------------------
%  INTRODUCTION
%-----------------------------------------------------------------------------
\input{intro}

\input{blockchain}

\input{design}

\input{apps}

%\input{mech}

\input{conclusion}

% One section per vertical.

% Core blockchain aspects. Smart Contract system. DataStore etc.

% Governance. Consensus, cryptoeconomics.

%-----------------------------------------------------------------------------
%  OVERALL DESIGN SECTION
%-----------------------------------------------------------------------------
%\input{design}

%----------------------------------------------------------------------------- BIBLIOGRAPHY
%-----------------------------------------------------------------------------
\section{Author Bio}

\noindent {\bf Arunesh Mishra:} Dr. Mishra has 10 years of research and development experience in the Industry in
Location and Mapping. At Google, he built the Location platform used widely on Android and Chrome and Google Maps
applications. He was the core designer for the crowdsourced algorithms that self-learn and power the location/mapping
for Google's mobile platform. The platform serves more than 2 Billion users daily. He holds a PhD, 30 issued patents and
22 pending patents today many of which are based on the physical layer mechanics of computing location and mapping. He
was won Best Paper awards at top ACM conferences and has over 30+ conference publications. He has widely contributed to
open source software used on standard Linux distributions today. He has also built the largest mobile peer-peer network
infrastructure for iOS/Android via Google Play Games offering.

\section{References}
\bibliography{latitude.bib}

\end{document}
