\section{Team}

Latitude has a highly competent team with a 20+ years of combined experience in the areas of location, ride sharing, mapping and
geo-spatial technologies. They have built some of the widely used products in the Industry today in these areas. They are well suited to take this plan to a successful execution.
\newline
\newline
\noindent
{\bf Jianming Zhou:}
Jianming is the CEO and co-Founder of SherpaShare, the leading driver assistant app to help ridesharing drivers to
maximize their earning potentials. He has more than 12 years of experience in the location industry. He was the founding
member of Alohar mobile(acquired by Alibaba group) and built the first Telematics engine used by MileIQ (acquired by
Microsoft). Previously, he was the engineering director at Loopt, the pioneer service in the mobile social local space
founded by Sam Altman. Before that, he was the engineer at Telenav which built the first turn-by-turn navigation system
on mobile devices. He holds an MS degree in Computer Science and majored in P2P network security and privacy.
\newline
\newline
\noindent
{\bf Tony Qin:}
Tony is AI Research Lead at DiDi Research America.  He established the reinforcement learning research at DiDi Chuxing
from scratch.  Previously, he was Staff Data Scientist at Walmart Labs.  Tony is an experienced and accomplished
scientist with a research background that intersects AI, machine learning, and optimization.  He has built numerous
successful AI and machine learning-powered solutions for ride-sharing and E-commerce domains.  He holds a Ph.D. in
Operations Research from Columbia University and has more than 15 conference and journal publications, 9 US patents, and
many more pending US and international patents.  He is an editorial board member and reviewer of various research
conferences and journals, and most recently, Senior Program Chair of AAAI 2019.
\newline
\newline
\noindent {\bf Colin Jia Zheng:}
Colin is the software engineer at Google working on distributed database system. He
holds a Ph.D degree in Computer Science from Harvard University and major in Cryptography.
\newline
\newline
\noindent {\bf Chanjun Yang:} Chanjun is the tech lead at Google Data Infrastructure Team. She has a MS degree in
Computer Science from ISU and a BS from Peking university. 
\newline
\newline
\noindent
{\bf Andrew Pillsbury:}
Andrew Pillsbury is VP Business Development for SherpaShare where he is responsible for B2B partnerships and sales. Previously he has held executive roles at The New Yorker Magazine and Macrovision (pre and post IPO). He has an MBA from The Wharton School and a BA from Duke University.
\newline
\newline
\noindent {\bf Jennifer Israel:}
Jen Israel is a passionate marketer with experience in integrated business to consumer marketing - brand, product,
marketing partnerships, customer relationship marketing, CPG and digital. Before joining SherpaShare as Head of
Marketing, Jen spent six years in fin-tech at Green Dot Corporation as the GoBank Mobile Bank Account brand and product
marketing leader directing strategic marketing planning, development, and execution.  Jen was responsible for launching
the first mobile bank account to be sold in Walmart, and the successful Uber Visa Debit Card, growing the program to
over 100,000 customers in the first year.
\newline
\newline
\noindent {\bf Arunesh Mishra (advisor) :} Dr. Mishra has 10 years of research and development experience in the Industry in
Location and Mapping. At Google, he built the Location platform used widely on Android and Chrome and Google Maps
applications. He was the core designer for the crowd-sourced algorithms that self-learn and power the location/mapping
for Google's mobile platform. The platform serves more than 2 Billion users daily. He holds a PhD, 30 issued patents and
22 pending patents today many of which are based on the physical layer mechanics of computing location and mapping. He
was won Best Paper awards at top ACM conferences and has over 30+ conference publications. He has widely contributed to
open source software used on standard Linux distributions today. He has also built the largest mobile peer-peer network
infrastructure for iOS/Android via Google Play Games offering.
